The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-07 paper.tex
update

\Cref{fig__gammaRaySynchtronSpectrum} shows the simulated microwave (left)\
and gamma-ray (right) spectra averaged over the different patches (shown in the legends) of the sky.\
The row from top to bottom shows the microwave (left) and gamma-ray (right) spectra\
with CRe spectral index $2.2, 2.4$ and $2.6$, respectively.\

We find that the simulated gamma-ray spectra are well fitted by\
the CRe spectral index 2.4 (the middle row),\
and display several similar features as observed.

First, the simulated and observed spectra of the \textit{Fermi} bubbles is\
nearly latitude independent, and characterized by a broad bump that roughly peaks around $\sim10$ GeV.\
However, the high-latitude spectrum tends to be slightly dimmer than low-latitude\
probably because the optical intensity in ISRF decays with increasing latitude.

Second, the gamma-ray spectra for all latitudes exhibit a spectral cutoff around energies 400--500 GeV,\
consistent with the observed cutoff energy.\
This is expected since
the upscattered high-energy photons ($\epsilon_{1}\sim450$ GeV) mainly arise from\
the relativistic scatterings between the high-energy CRe ($\gtrapprox 408$ GeV)\
and optical starlight ($\epsilon \sim 10$ eV),\
and therefore \Cref{gamma-min} can be reduced to $\epsilon_{1}\sim\gamma m_{\text{e}}c^2$\
in the Klein--Nishina limit\
$\left(\text{i.e. }\epsilon_{1}\epsilon \gg \left(m_{\text{e}}c^2\right)^2\right)$,\
implying most of the CRe energy is carried away by the upscattered photons.

@@

@@

  We display the morphology of the \textit{Fermi} bubbles\
  that emit gamma-rays from the inverse Compton scattering of ISRF by CRe.

>>>>

\Cref{fig__gammaRaySynchtronSpectrum} shows the simulated microwave (left)\
and gamma-ray (right) spectra averaged over the different patches (shown in the legends) of the sky.\
The row from top to bottom shows the microwave (left) and gamma-ray (right) spectra\
with CRe spectral index $2.2, 2.4$ and $2.6$, respectively.\
Several points are worth specific comment.\

First, we find that the simulated gamma-ray spectra are well fitted by\
the CRe spectral index 2.4 (the middle row),\
even simulated microwave spectra are marginally consistent with the observed.

Second, the simulated and observed gamma-ray spectra is\
nearly latitude independent, and characterized by a broad bump that roughly peaks around $\sim10$ GeV.\
However, the high-latitude spectrum tends to be slightly dimmer than low-latitude\
probably because the optical intensity in ISRF decays with increasing latitude.

Third, the gamma-ray spectra for all latitudes indicate a spectral cutoff around energies 400--500 GeV,\
consistent with the observed cutoff energy.\
This is expected since
the upscattered high-energy photons ($\epsilon_{1}\sim450$ GeV) mainly arise from\
the scatterings between the relativistic CRe ($\gtrapprox 408$ GeV)\
and optical starlight ($\epsilon \sim 10$ eV),\
and therefore \Cref{gamma-min} can be reduced to $\epsilon_{1}\sim\gamma m_{\text{e}}c^2$\
in the Klein--Nishina limit\
$\left(\text{i.e. }\epsilon_{1}\epsilon \gg \left(m_{\text{e}}c^2\right)^2\right)$,\
implying most of the CRe energy is carried away by the upscattered photons.

Fourth, the good agreement between the simulated and observed gamma-ray/microwave spectra\
imply that the emission of the Fermi bubbles and\
the microwave haze can be produced by the same high-energy electrons\
via inverse Compton scatterings and synchrotron radiations\
in the presence of ISRF and magnetic fields, respectively,\
as previously suggested \citep{Su2010,Dobler2012}.

@@

 Finally, we display the morphology of the \textit{Fermi} bubbles\
 that emit gamma-rays from the inverse Compton scattering of ISRF by CRe\
 with the best-fit CRe sptral index 2.4

@@
